A smart street lighting system based on \rev{an} IPv6-enabled wireless sensor network

### 2014-11-21 2014_ELSEVIER_CEE_SI/paper_cee_special_issue.tex
Melhorando a introdução

>>>>

\rev{With  the increase in world population and the growing urbanization worldwide, cities will need to evolve towards an intelligent infrastructure in order to provide to its citizens a better living environment. This will be achieved through the use of information and communication technology (ICT), with the goal to provide public services that are more accessible and more efficient. This vision is embodied in the "smart city" concept. (A Smart City and the Applications, 2011, Global Perspective of Smart Cities: A Survey, 2013).}

\rev{According to several researchers, to enable the smart city it will be required an urban "Internet of Things(IoT)" infrastructure. (Developing an IoT Smart City Framework, Internet of Things for Smart Cities, An Information Framework for Creating a Smart City Through Internet of Things, Padova Smart City: an Urban Internet of Things Experimentation, A Generic IoT Architecture for Smart Cities).}

%Applications of a smart city: structural health, waste management, air quality monitoring, noise monitoring, traffic congestion, city energy consumption, smart parking, smart lighting, charging infrastructure for electrical vehicles, creation of bike lane network to promote emission-free transport, City-wide wiring and sensorization for environmental data collection in order to analyse factors like pedestrian and car traffic, energy demand, crowd gathering, etc., with the main goal of improving citizens? quality of life.

\rev{Smart street lighting system has become the foundation in the development of smart cities. Regarding to cities, street lights are one of the most important assets to maintain and control, providing safe roads, inviting public areas, and enhancing security in homes, businesses, and city centers. However, this concrete asset is very costly to operate, with a share of about 40\% of the total amount of electricity spent in a city. This factor, together with the continuous rising of electricity costs, is becoming more and more crucial day by day for the budget of a city. (Smart Lighting solutions for Smart Cities, 2013).}

%These solutions are being powered with the embedded Internet Protocol connectivity, making thereby feasible
%an end-to-end connectivity between the smart phones and the lights. Thereby, the IP-based capabilities are opening a great number of opportunities for the integration with applications from external developers, and third party consumer devices.
